\section{USSD Supply management}

USSD coin is 'initialized' with one-time minting of 1000 USSD, taking 1000 DAI as collateral. 
This 1000 USSD would allow to create a pool USSD/DAI to have initial liquidity. Uniswap V3 
is selected as DEX of choice on Ethereum for being largest in volume and long-time reliable 
solution for on-chain swaps. As the pair is consisting of two stablecoins, the minimal fee 
tier (0.05\%) is used. Initial liquidity equation at the whole price range would be:

\[ {P_{USSD} \cdot P_{DAI} = 1}, \]

assuming equal price of USSD and DAI as a regular AMM curve that should fit the purpose 
of price discovery. Other curve variants, such as constant price () or Stableswap invariant 
(https://classic.curve.fi/files/stableswap-paper.pdf) serve different purposes (e.g. to 
prevent slippage when having a pool of stablecoins, even with significant different in 
their amounts).

The pool is used for price discovery of USSD, avoiding the necessity to use any off-chain\
oracles to keep USSD as autonomous as possible. For protection against flash-loan or 
liquidity manipulation geometric mean price oracle from Uniswap V3 is used 
(https://uniswap.org/whitepaper-v3.pdf):

\[ P_{ t1,t2 } = 1.0001^{ { a_{t2}-a_{t1} } \over {t_2 - t_1} }, \]

where t2 and t1 are define interval in seconds, and at1, at2 define accumulator values. 
The length of the interval could be fine-tuned, making the assumed price less susceptible 
for short-term fluctuations (and liquidity/loan attacks), gaining some latency, but spending 
less gas overall on rebalancing operations.

The main way to obtain the USSD would be buying it on the USSD/DAI pool, this would increase 
the price of USSD in comparison to DAI. In such scenario, two outcomes are possible: 
the price is arbitraged back (and nothing changes to the supply) or USSD rebalances itself, 
minting USSD and selling it for DAI on the pool, expanding the total supply of USSD.

In the opposite scenario (price of USSD goes below 1 DAI), USSD contract would reduce supply, 
using stored collateral to buy USSD back and burn it, reducing total supply of USSD and 
bringing the peg back to 1 DAI.

